---
title: "HW191108"
output: 
   html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(forcats)
library(stringr)
library(lubridate)
library(nycflights13)
```

#Factor

##GSS

###Q1

```{r}
rincome_plot <-
  gss_cat %>%
  ggplot(aes(x = rincome)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
rincome_plot
```

###Q2

```{r}
gss_cat %>%
  count(relig) %>%
  arrange(desc(n)) 
```

```{r}
gss_cat %>%
  count(partyid) %>%
  arrange(desc(n))
```

###Q3

```{r}
gss_cat %>%
  filter(!denom %in% c(
    "No answer", "Other", "Don't know", "Not applicable",
    "No denomination"
  )) %>%
count(relig)
```

##Modifying factor order

###Q1

```{r}
gss_cat %>%
  filter(!is.na(tvhours)) %>%
  ggplot(aes(x = tvhours)) +
  geom_histogram(binwidth = 1)
```

It's skewed to the right, so median is a better indicator.

###Q2

```{r}
keep(gss_cat, is.factor) %>% names()
```

The order of the rincome and partyid can be principled; others are basically arbitrary.

##Modifying factor levels

###Q1

```{r}
gss_cat %>%
  mutate(partyid = fct_collapse(partyid, 
    other = c("No answer", "Don't know", "Other party"),
    rep = c("Strong republican", "Not str republican"),
    ind = c("Ind,near rep", "Independent", "Ind,near dem"),
    dem = c("Not str democrat", "Strong democrat"))) %>%
  count(year, partyid) %>%
  group_by(year) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(year, prop, colour = fct_reorder2(partyid, year, prop))) +
  geom_point() +
  geom_line() +
  labs(colour = "Party ID.")
```

###Q2

```{r}
gss_cat %>%
  mutate(rincome = fct_collapse(rincome, 
        `Unknown` = c("No answer", "Don't know", "Refused", "Not applicable"),
        `Lt $5000` = c("Lt $1000", str_c("$", c("1000", "3000", "4000"), " to ", c("2999", "3999", "4999"))),
        `$5000 to 10000` = str_c("$", c("5000", "6000", "7000", "8000"), " to ", c("5999", "6999", "7999", "9999")))
  ) %>%
  ggplot(aes(x = rincome)) +
  geom_bar() +
  coord_flip()
```

#Date/Time

```{r}
make_datetime_100 <- function(year, month, day, time) {
  make_datetime(year, month, day, time %/% 100, time %% 100)
}

flights_dt <- flights %>%
  filter(!is.na(dep_time), !is.na(arr_time)) %>%
  mutate(
    dep_time = make_datetime_100(year, month, day, dep_time),
    arr_time = make_datetime_100(year, month, day, arr_time),
    sched_dep_time = make_datetime_100(year, month, day, sched_dep_time),
    sched_arr_time = make_datetime_100(year, month, day, sched_arr_time)
  ) %>%
  select(origin, dest, ends_with("delay"), ends_with("time"))
```

##Create Date/Time

###Q1

```{r}
ret <- ymd(c("2010-10-10", "bananas"))
ret
```

###Q2

```{r}
today(tzone = "EST")
```

###Q3

```{r}
d1 <- "January 1, 2010"
mdy(d1)
d2 <- "2015-Mar-07"
ymd(d2)
d3 <- "06-Jun-2017"
dmy(d3)
d4 <- c("August 19 (2015)", "July 1 (2015)") 
mdy(d4)
d5 <- "12/30/14"
mdy(d5)
```

##Component

```{r}
sched_dep <- flights_dt %>%
  mutate(minute = minute(sched_dep_time)) %>%
  group_by(minute) %>%
  summarise(avg_delay = mean(arr_delay, na.rm = TRUE), n = n())
```

###Q1

```{r}
flights_dt %>%
  filter(!is.na(dep_time)) %>%
  mutate(dep_hour = update(dep_time, yday = 100)) %>%
  mutate(month = factor(month(dep_time))) %>%
  ggplot(aes(dep_hour, color = month)) +
  geom_freqpoly(binwidth = 60 * 60)
```

###Q2

```{r}
flights_dt %>%
  mutate(dep_time_ = sched_dep_time + dep_delay * 60) %>%
  filter(dep_time_ != dep_time) %>%
  select(dep_time_, dep_time, sched_dep_time, dep_delay)
```

The date is different.

###Q3

```{r}
flights_dt %>%
  mutate(flight_duration = as.numeric(arr_time - dep_time), air_time_mins = air_time, diff = flight_duration - air_time_mins) %>%
  select(origin, dest, flight_duration, air_time_mins, diff)
```

###Q4

```{r}
flights_dt %>%
  mutate(sched_dep_hour = hour(sched_dep_time)) %>%
  group_by(sched_dep_hour) %>%
  summarise(dep_delay = mean(dep_delay)) %>%
  ggplot(aes(y = dep_delay, x = sched_dep_hour)) +
  geom_point() +
  geom_smooth()
```

Avoid afternoon flights.

###Q5

```{r}
flights_dt %>%
  mutate(dow = wday(sched_dep_time, label = T)) %>%
  group_by(dow) %>%
  summarise(
    dep_delay = mean(dep_delay),
    arr_delay = mean(arr_delay, na.rm = TRUE)
  ) %>%
  ggplot() +
  geom_bar(aes(x = dow, y = dep_delay), stat = "identity") 
```

###Q6

```{r}
ggplot(flights_dt, aes(x = minute(sched_dep_time))) +
  geom_histogram(binwidth = 1)
```

```{r}
ggplot(diamonds, aes(x = carat %% 1 * 100)) +
  geom_histogram(binwidth = 1)
```
Peaks at nice values.

###Q7

```{r}
flights_dt %>%
  mutate(minute = minute(dep_time), early = dep_delay < 0) %>%
  group_by(minute) %>%
  summarise(early = mean(early, na.rm = TRUE), n = n()) %>%
  ggplot(aes(minute, early)) +
  geom_line()
```

##Time spans

###Q1

Because there isn't a fixed value of days in each month.

###Q2

`overnight` is either true or false; if it is true, the add one more day.

###Q3

```{r}
ymd("2015-01-01") + months(0:11)
```

```{r}
floor_date(today(), unit = "year") + months(0:11)
```

###Q4

```{r}
age <- function(bday) {
  (bday %--% today()) %/% years(1)
}
age(ymd("2002-10-23"))
```

###Q5

It's missing a parentheses before the slash
```{r}
(today() %--% (today() + years(1))) / months(1)
```
