---
title: "HW191028"
output:
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
library(stringi)
```

##String Basics

###Q1

```{r}
paste("hello", "Helen")
paste0("hello", "Helen")
str_c("hello", "Helen")
```

```{r}
paste("hello", NA)
paste0("hello", NA)
str_c("hello", NA)
```

###Q2

`sep` is used to seperate elements in a string by inserting a string of seperator, while `collapse` separates elements of the character vector into a character vector of length one.

###Q3

```{r}
x <- c("a", "abc", "abcd", "abcde", "abcdef")
L <- str_length(x)
m <- ceiling(L / 2)
str_sub(x, m, m)
```

###Q4

```{r}
str_wrap("let me see what is the use of this function", width = 6)
```

###Q5

```{r}
str_trim(" ab c ")
str_trim(" abc ", side = "left")
```

```{r}
str_pad("abc", 4, side = "right")
str_pad("abc", 4)
str_pad("abc", 5)
str_pad("abc", 5, side = "both")
```

###Q6

```{r}
str_commasep <- function(x) {
  n <- length(x)
  if (n == 0) {
    ""
  } else if (n == 1) {
    x
  } else if (n == 2) {
    str_c(x[[1]], "and", x[[2]], sep = " ")
  } else {
    not_last <- str_c(x[seq_len(n - 1)], ",")
    # prepend "and" to the last element
    last <- str_c("and", x[[n]], sep = " ")
    # combine parts with spaces
    str_c(c(not_last, last), collapse = " ")
  }
}
str_commasep(c("a", "b", "c"))
```

##Matching

###Basic Match

####Q1

`\` escapes next character; `\\` gives a literary "\"; `\\\` gives a "\" and escapes the next character.

####Q2

```{r}
str_view("\"'\\", "\"'\\\\", match = TRUE)
```

####Q3

```{r}
str_view(c(".a.b.c", ".a.b", "....."), c("\\..\\..\\.."), match = TRUE)
```

###Anchor

####Q1

```{r}
str_view(c("$^$", "ab$^$sfas"), "^\\$\\^\\$$", match = TRUE)
```

####Q2

```{r}
str_view(stringr::words, "^y", match = TRUE)
str_view(stringr::words, "x$", match = TRUE)
str_view(stringr::words, "^...$", match = TRUE)
str_view(stringr::words, ".......", match = TRUE)
```

###Character classes

####Q1

```{r}
str_subset(stringr::words, "^[aeiou]")
```

```{r}
str_subset(stringr::words, "^[^aeiou]+$")
```

```{r}
str_subset(stringr::words, "[^e]ed$")
```

```{r}
str_subset(stringr::words, "i(ng|se)$")
```

####Q2

```{r}
str_subset(stringr::words, "(cie|[^c]ei)")
```

```{r}
str_subset(stringr::words, "(cei|[^c]ie)")
```

####Q3

```{r}
str_subset(stringr::words, "q[^u]")
```

####Q4

```{r}
str_subset(stringr::words, "ou|ise$|ae|oe|yse$")
```

####Q5

```{r}
phone <- "609-933-3471"
str_view(phone, "\\d\\d\\d-\\d\\d\\d-\\d\\d\\d\\d")
```

```{r}
str_view(phone, "[0-9][0-9][0-9]-[0-9][0-9][0-9]-[0-9][0-9][0-9][0-9]")
```

###Repetition

####Q1

`?` equals `{0,1}`; `+` equals `{1,}`; `*` equals`{0,}`.

####Q2

`^.*$` matches everything.
`"\\{.+\\}"` matches strings with {} and something within.
`\d{4}-\d{2}-\d{2}`matches strings with 4digits-2digits-2digits.
"\\\\{4}" matches four backslashes.

####Q3

```{r}
str_view(words, "^[^aeiou]{3}", match = TRUE)
```

```{r}
str_view(words, "[aeiou]{3,}", match = TRUE)
```

```{r}
str_view(words, "([aeiou][^aeiou]){2,}", match = TRUE)
```

###Grouping & Backreferences

####Q1

`(.)\1\1` a same character appears three times.
`"(.)(.)\\2\\1"` abba
`(..)\1` abab
`"(.).\\1.\\1"` abaca
`"(.)(.)(.).*\\3\\2\\1"` abcd(sth here)cba

####Q2

```{r}
str_subset(words, "^(.).*\\1$")
```

```{r}
str_subset(words, "(.)(.).*\\1\\2")
```

```{r}
str_subset(words, "(.).*\\1.*\\1")
```

##Tools

###Detect

####Q1

```{r}
words[str_detect(words, "^x|x$")]
str_subset(words, "^[aeiou].*[^aeiou]$") %>% head()
```

```{r}
pattern <- cross(rerun(5, c("a", "e", "i", "o", "u")),
    .filter = function(...) {
      x <- as.character(unlist(list(...)))
      length(x) != length(unique(x))
    }
  ) %>%
  map_chr(~ str_c(unlist(.x), collapse = ".*")) %>%
  str_c(collapse = "|")
str_subset(words, pattern)
```

```{r}
words[str_detect(words, "a") &
  str_detect(words, "e") &
  str_detect(words, "i") &
  str_detect(words, "o") &
  str_detect(words, "u")]
```

###Extract

####Q1

```{r}
colours <- c("red", "orange", "yellow", "green", "blue", "purple")
color_match <- str_c(colours, collapse = "|") 
color_match2 <- str_c("\\b(", str_c(colours, collapse = "|"), ")\\b")
more2 <- sentences[str_count(sentences, color_match) > 1]
str_view_all(more2, color_match2, match = TRUE)
```

####Q2

```{r}
pattern <- "\\b[A-Za-z]+ing\\b"
sentences_with_ing <- str_detect(sentences, pattern)
unique(unlist(str_extract_all(sentences[sentences_with_ing], pattern))) %>%
  head()
```

```{r}
unique(unlist(str_extract_all(sentences, "\\b[A-Za-z]{3,}s\\b"))) %>%
  head()
```

###Grouped matches

####Q1

```{r}
numword <- "\\b(one|two|three|four|five|six|seven|eight|nine|ten) +(\\w+)"
sentences[str_detect(sentences, numword)] %>%
  str_extract(numword)
```

####Q2

```{r}
contraction <- "([A-Za-z]+)'([A-Za-z]+)"
sentences[str_detect(sentences, contraction)] %>%
  str_extract(contraction) %>%
  str_split("'")
```

###Replacing

####Q1

```{r}
str_replace_all("past/present/future", "/", "\\\\")
```

####Q2

```{r}
replacements <- c(
  "A" = "a", "B" = "b", "C" = "c", "D" = "d", "E" = "e",
  "F" = "f", "G" = "g", "H" = "h", "I" = "i", "J" = "j",
  "K" = "k", "L" = "l", "M" = "m", "N" = "n", "O" = "o",
  "P" = "p", "Q" = "q", "R" = "r", "S" = "s", "T" = "t",
  "U" = "u", "V" = "v", "W" = "w", "X" = "x", "Y" = "y",
  "Z" = "z"
)
lower_words <- str_replace_all(words, pattern = replacements)
head(lower_words)
```

####Q3

```{r}
swapped <- str_replace_all(words, "^([A-Za-z])(.*)([a-z])$", "\\3\\2\\1")
intersect(swapped, words)
```

###Splitting

####Q1

```{r}
x <- c("apples, pears, and bananas")
str_split(x, ", +(and +)?")[[1]]
```

####Q2

```{r}
sentence <- "The quick (???brown???) fox can???t jump 32.3 feet, right?"
str_split(sentence, boundary("word"))
```

####Q3

```{r}
str_split("ab. cd|agt", "")
```

```{r}
str_locate("The quick (???brown???) fox can???t jump 32.3 feet, right?", "ju")
```

##Other patterns

###Q1

```{r}
str_subset(c("a\\b", "ab"), "\\\\")
str_subset(c("a\\b", "ab"), fixed("\\"))
```

###Q2
```{r}
tibble(word = unlist(str_extract_all(sentences, boundary("word")))) %>%
  mutate(word = str_to_lower(word)) %>%
  count(word, sort = TRUE) %>%
  head(5)
```

##Stringi

###Q1

```{r}
stri_count_words(head(sentences))
stri_duplicated(c(
  "the", "brown", "cow", "jumped", "over",
  "the", "lazy", "fox"
))
stri_rand_strings(4, 5)
```

