---
title: "HW0921_He Jiang"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library(nycflights13)
```

#Workflow: Basics
###1.
```{r, eval=FALSE}
my_variable <- 10
#my_var??able
```
Because the object called("my_var??able") is different from the object assigned("my_variable") with the value.
###2.
```{r}
ggplot(data = mpg) +
         geom_point(mapping = aes(x = displ, y = hwy))
```
change "dota" to "data"
```{r}
filter(mpg, cyl == 8)
```
change "fliter" to "filter"; change "=" to "=="
```{r}
filter(diamonds, carat > 3)
```
change "diamond" to "diamonds"
###3
"Alt-Shift-K" shows all the shortcuts; "Tools" --> "Keyboard Shortcuts Help"

#Data Transformation with dplyr
##Filter
###1
```{r}
flights
#?flights
```

```{r}
filter(flights, arr_delay > 120)
```

```{r}
filter(flights, dest == "IAH" | dest == "HOU")
```

```{r}
filter(flights, carrier == "UA" | carrier == "AA" | carrier == "DA")
```

```{r}
filter(flights, month < 9 & month > 5)
```

```{r}
filter(flights, arr_delay > 120 &! dep_delay > 0)
```

```{r}
filter(flights, dep_delay >= 60 & air_time > 30)
```

```{r}
filter(flights, dep_time >= 0 & dep_time <= 600)
```
###2
between() can be used to find values in an inclusive range;
```{r}
filter(flights, between(dep_time, 0, 600))
```
###3
8255, arr_delay, dep_delay, arr_time, air_time
```{r}
filter(flights, is.na(dep_time))
count(filter(flights, is.na(dep_time)))
```
###4
```{r}
NA ^ 0
NA | TRUE
NA | FALSE
FALSE & NA
TRUE & NA
```

##Arrange
###1
*Interesting*
```{r}
arrange(flights, desc(is.na(dep_time)), dep_time)
```
###2
```{r}
arrange(flights, desc(dep_delay))
```

```{r}
arrange(flights, dep_delay)
```
###3
```{r}
arrange(flights, air_time)
```
###4
```{r}
arrange(flights, desc(distance))
```

```{r}
arrange(flights, distance)
```

##Select
###1
```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)
select(flights, (dep_time:arr_delay))
select(flights, -(year:day), -(carrier:time_hour))
```
###2
```{r}
select(flights, year, year)
```
That variable will only appear once.
###3
```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, one_of(vars))
```
It selects the variables in the vector and can be found in "flights"
```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay", "time")
select(flights, one_of(vars))
```
###4
```{r}
select(flights, contains("TIME"))
```
It gives all the variables related to time even though no variable is called "TIME". They contains the word "time"
```{r}
select(flights, contains("TIME", ignore.case = FALSE))
```

##Mutate
###1
```{r}
transmute(flights, dep_time, time_in_min = dep_time %/% 100 * 60 + dep_time %% 100)
```
###2
air_time should equal to time. 
```{r}
transmute(flights, air_time, time = arr_time - dep_time)
```
different units.
```{r}
transmute(flights, air_time, time = arr_time %/% 100 * 60 + arr_time %% 100 - dep_time %/% 100 *60 - dep_time %% 100)
```
###3
```{r}
transmute(flights, sched_dep_time, dep_time, dep_delay, delay = dep_time %/% 100 *60 + dep_time %% 100 - sched_dep_time %/% 100 *60 - sched_dep_time %% 100)
```
###4
*interesting*
```{r, eval = FALSE}
df <- (flights, (desc(dep_delay))
 min_rank(df$dep_delay)
```
###5
it returns a string of length 10 w/ 1:3 cycled
```{r}
1:3 + 1:10
```
###6
cos(x)
sin(x)
tan(x)

acos(x)
asin(x)
atan(x)
atan2(y, x)

cospi(x)
sinpi(x)
tanpi(x)
```{r}
?Trig
```

##Summarize
###1
*interesting*
```{r}
flight_delay_summary <- group_by(flights, flight) %>% summarise(num_flights = n(), percentage_on_time = sum(arr_time == sched_arr_time)/num_flights, percentage_early = sum(arr_time < sched_arr_time)/num_flights, percentage_15_mins_early = sum(sched_arr_time - arr_time == 15)/num_flights, percentage_late = sum(arr_time > sched_arr_time)/num_flights,percentage_15_mins_late = sum(arr_time - sched_arr_time == 15)/num_flights, percentage_2_hours_late = sum(arr_time - sched_arr_time == 120)/num_flights, rm.na = TRUE)
flight_delay_summary
flight_delay_summary %>% filter(percentage_15_mins_early == 0.5 & percentage_15_mins_late == 0.5)
```
###2
```{r}
not_cancelled <- flights %>%
filter(!is.na(dep_delay), !is.na(arr_delay))
not_cancelled %>%
  count(dest)
not_cancelled %>%
  group_by(dest) %>%
  summarise(n = length(dest))
```

```{r}
not_cancelled %>%
  count(tailnum, wt = distance)
not_cancelled %>%
  group_by(tailnum) %>%
  summarise(n = sum(distance))
```
###3
because arr_delay is more important
###4
```{r}
cancelled_day <- flights %>%
mutate(cancelled = (is.na(arr_delay) | is.na(dep_delay))) %>%
group_by(year, month, day) %>%
summarise(cancelled_num = sum(cancelled), flights_num = n())
cancelled_day
ggplot(cancelled_day) +
  geom_point(aes(x = cancelled_num, y = flights_num))
```
###5
```{r}
flights %>%
  group_by(carrier) %>%
  summarize(arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(desc(arr_delay))
```
###6
*interesting*
```{r}
num_delay <- flights %>%
    group_by(tailnum) %>%
    arrange(time_hour) %>%
    mutate(yes = cumall(dep_delay < 60)) %>%
    filter(yes == TRUE) %>%
  tally(sort = TRUE) 
num_delay
ggplot(num_delay)+
  geom_histogram(mapping = aes(x = n), boundary = 0)
```
###7
sort() to count() sort by descending order; it shows the most common group first.

##Grouping
###1
?
###2
```{r}
flights %>%
  group_by(tailnum) %>%
  summarise(arr_delay = mean(arr_delay)) %>%
  filter(min_rank(desc(arr_delay)) == 1)
```
###3
```{r}
flights %>%
  group_by(hour) %>%
  summarise(arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(arr_delay)
```
###4
```{r}
flights %>%
  group_by(dest) %>%
  filter(!is.na(arr_delay)) %>%
  mutate(total_delay = sum(arr_delay), airline_delay = arr_delay / total_delay) %>%
  select(year:day, dest, arr_delay, total_delay, airline_delay) %>%
  arrange(dest, desc(airline_delay))
```
###5
```{r}
lagged_delays <- flights %>%
  group_by(origin) %>%
  mutate(dep_lag = lag(dep_delay)) %>%
  filter(!is.na(dep_delay)) %>%
  group_by(origin, dep_lag) %>%
  summarise(dep_mean = mean(dep_delay)) %>%
  arrange(origin, dep_mean) 
lagged_delays
```
###6
```{r}
flights %>%
  group_by(dest) %>%
  mutate(speed = distance / air_time) %>%
  arrange(speed) %>%
  select(tailnum, distance, air_time, speed) 
```

```{r}
flights %>%
  group_by(dest) %>%
  mutate(shortest = air_time - min(air_time, na.rm = T)) %>%
  arrange(air_time) %>%
  select(tailnum, sched_dep_time, sched_arr_time, shortest)
```
###7
```{r}
flights %>%
  group_by(dest) %>%
  filter(n_distinct(carrier) > 2) %>%
  group_by(carrier) %>%
  summarise(n = n_distinct(dest)) %>%
  arrange(desc(n))
```


