---
title: "Reading191019"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nycflights13)
```

#Ch. 9

##Gather and spread
```{r}
table4a %>%
    gather(`1999`, `2000`, key = "year", value = "cases")
```

```{r}
table2
spread(table2, key = type, value = count)
```

##Seperate and unite
```{r}
table3 %>%
    separate(rate, into = c("cases", "population"))
table3 %>%
    separate(rate, into = c("cases", "population"), sep = "/", convert = T)
```

```{r}
table5
table5 %>%
    unite(Year, century, year)
table5 %>%
    unite(Year, century, year, sep = "")
```

```{r}
tibble(x = c("X1", "X2", "Y1", "Y2")) %>%
  separate(x, c("variable", "into"), sep = c(1))
```
Because the inputs are characters, sep =1 --> sep =c(1)

###Extract
```{r}
tibble(x = c("X_1", "X_2", "AA_1", "AA_2")) %>%
  extract(x, c("variable", "id"), regex = "([A-Z])_([0-9])")
tibble(x = c("X11", "X2", "AA1", "AA2")) %>%
  extract(x, c("variable", "id"), regex = "([A-Z]+)([0-9]+)")
```

##Missing values
```{r}
stocks <- tibble(
year =c(2015,2015,2015,2015,2016,2016,2016), qtr =c( 1, 2, 3, 4, 2, 3, 4), return=c(1.88,0.59,0.35, NA,0.92,0.17,2.66)
)
```
explicit missing: NA
implicit missing: e.g. 2016.1
```{r}
stocks %>%
spread(year, return) %>%
gather(year, return, `2015`:`2016`, na.rm = TRUE)
```

```{r}
stocks %>%
    complete(year, qtr)
```

###When NA means previous value carries forward
```{r}
treatment <- tribble(
~ person, ~ treatment, ~response, "Derrick Whitmore", 1, 7,
NA, 2, 10,
NA, 3, 9, "Katherine Burke", 1, 4
)
```

```{r}
treatment %>%
  fill(person)
```

##WHO case study
```{r}
who1 <- who %>%
  gather(new_sp_m014:newrel_f65, key = "key", value = "cases",
na.rm = TRUE) %>%
  select(-iso2, -iso3) %>%
  mutate(key = stringr::str_replace(key, "newrel", "new_rel")) %>%
  separate(key, c("new", "type", "sexage"), sep = "_") %>%
  select(-new) %>%
  separate("sexage", c("sex", "age"), sep = 1)
who1
```

#Ch. 10 Relational data

##nycflights
```{r}
flights_latlon <- flights %>%
  inner_join(select(airports, origin = faa, origin_lat = lat, origin_lon = lon),
    by = "origin"
  ) %>%
  inner_join(select(airports, dest = faa, dest_lat = lat, dest_lon = lon),
    by = "dest"
  )
```


```{r}
flights_latlon %>%
  slice(1:100) %>%
  ggplot(aes(
    x = origin_lon, xend = dest_lon,
    y = origin_lat, yend = dest_lat
  )) +
  borders("state") +
  geom_segment(arrow = arrow(length = unit(0.1, "cm"))) +
  coord_quickmap() +
  labs(y = "Latitude", x = "Longitude")
```

##Mutating Joins

```{r}
flights2 <- flights %>%
    select(year:day, hour, origin, dest, tailnum, carrier)
 flights2 %>%
    select(-year, -origin, -dest) %>%
    left_join(airlines, by = "carrier")
```
can be achieved using mutating
```{r}
flights2 %>%
    select(-year, -origin, -dest) %>%
    mutate(name = airlines$name[match(carrier, airlines$carrier)])
```

###Inner-joins
```{r}
 x <- tribble(~key, ~val_x,
              1, "x1",
              2, "x2",
              3, "x3")
 y <- tribble(~key, ~val_y,
              1, "y1",
              2, "y2",
              4, "y3")
```

```{r}
x %>%
  inner_join(y, by = "key")
```

###Outer-joins
keep observation that appear in both tables
left: keep all in x; right: keep all in y; full: keep all
```{r}
x %>%
  full_join(y, by = "key")
```

###Natural join
match the common variables.
```{r}
flights2 %>%
  left_join(weather)
```

