---
title: "0921classnote"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nycflights13)
library(dplyr)
```

#HW
mutate, ex.4
```{r}
df <- tibble(c1 = letters [1:3], c2 = c(30, 45, 40))
min_rank(df$c2)
```

```{r}
flights_delayed <- mutate(flights, dep_delay_min_rank = min_rank(desc(dep_delay)))
flights_delayed1 <- filter(flights_delayed, dep_delay_min_rank <= 10)
arrange(flights_delayed1, dep_delay_min_rank)
```

group, ex.7
```{r}
num_delay <- flights %>%
    group_by(tailnum) %>%
    arrange(time_hour) %>%
    mutate(yes = cumall(dep_delay < 60)) %>%
    filter(yes == TRUE) %>%
  tally(sort = TRUE) 
num_delay
ggplot(num_delay)+
  geom_histogram(mapping = aes(x = n), boundary = 0)
```

understand what to code

#Github
Change to html_document,
Go to setting -> output option.. -> advanced -> keep markdown source files
Commit changes in Github desktop, push to origin.
Now md file on Github is readable.
("Commit" saves the file to local, "Push" saves the file online)

#import packages into R
readr, lubridate
vignette (short description of packages)
```{r}
data =read.csv("Fraud_Data.csv")
```


#final project
nyc open data, kaggle