---
title: "Fraud_data_exploration"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(readr)
```

# Fraud Data Exploration
Import data:
```{r}
Fraud <- read_csv("Fraud/Fraud_Data.csv")
```

## General Info
Types of variables?
```{r}
names(Fraud)
```
Number of observation?
```{r}
nrow(Fraud)
```
How many frauds in total?
```{r}
group_by(Fraud, class) %>%
  count()
```
##Browsers
What types of browser?
```{r}
Browser <- select(Fraud, browser)
unique(Browser)
```
###Which browser has the most fraud?
Table:
```{r}
brow <- group_by(Fraud, browser, class) %>%
  count()%>%
  ungroup() %>%
  mutate(class = as.factor(class))
brow
```
Graphs:
```{r}
ggplot(brow) +
  geom_bar(stat = "identity", aes(x = reorder(browser, -n), y = n, fill = class), position = "dodge")
```
###Which browser has the highest percentage of frauds?
```{r}
ggplot(brow) +
  geom_bar(stat = "identity", aes(x = reorder(browser, n), y = n, fill = class), position = "fill")
```

```{r}
ggplot(brow) +
  geom_bar(stat = "identity", aes(x = reorder(browser, n), y = n, fill = class), position = "fill") +
  coord_cartesian(ylim = c(0, 0.15))
```
So we can see that Chrome has the highest.
##Age and Sex
###General:
Age:
```{r}
Age <- select(Fraud, age)
summary(Age)
```
Visualization
```{r}
ggplot(Fraud) +
  geom_histogram(aes(x = age, binwidth = 1))
```
Sex: 
```{r}
Sex <- select(Fraud, sex)
group_by(Fraud, sex) %>%
  count()
```
Visualization
```{r}
ggplot(Fraud) +
  geom_bar(aes(x = sex))
```
###Relation between Age and sex
```{r}
AgeSex <- select(Fraud, sex, age, class)
Maleage <- filter(AgeSex, sex == "M") %>%
  summary(age)
Femaleage <- filter(AgeSex, sex =="F") %>%
  summary(age)
Maleage
Femaleage
```
Female has a lower mean, but the maximum is hight. Females experience 9.1% fraud, while males experience 9.6%.

Visualization
```{r}
ggplot(Fraud) +
  geom_boxplot(aes(x = sex, y = age))
```
###Frauds distribution within sex & age groups
This shows the amount of frauds in each sex group.
```{r}
agesex <- group_by(Fraud, sex, age, class) %>%
  count()%>%
  ungroup() %>%
  mutate(class = as.factor(class))
ggplot(agesex) +
  geom_bar(stat = "identity", aes(x = sex, y = n, fill = class), position = "dodge")
```
these graphs show the proportion of frauds in each sex group. Males have relatively more frauds.
```{r}
ggplot(agesex) +
  geom_bar(stat = "identity", aes(x = sex, y = n, fill = class), position = "fill")
```

```{r}
ggplot(agesex) +
  geom_bar(stat = "identity", aes(x = sex, y = n, fill = class), position = "fill") +
  coord_cartesian(ylim = c(0, 0.13))
```
This shows the number of frauds in each age group. 
```{r}
ggplot(agesex) +
  geom_bar(stat = "identity", aes(x = age, y = n, fill = class), position = "dodge") 
```

```{r}
ggplot(agesex) +
  geom_bar(stat = "identity", aes(x = age, y = n, fill = class), position = "fill") 
```
One age group has relatively high proportion. Which is..
```{r}
agefrauds <-group_by(Fraud, age, class) %>%
  count()%>%
  ungroup() %>%
  mutate(class = as.factor(class)) %>%
  filter(class == 1)
arrange(agefrauds, desc(n))
```
36.
if we just want to find which sex-age group has the highest frauds: 
```{r}
frauds <- filter(agesex, class == 1)
arrange(frauds, desc(n))
```
male, 32
##Purchase value
###General
quick summary
```{r}
val <- group_by(Fraud, purchase_value, class) %>%
  count()%>%
  ungroup() %>%
  mutate(class = as.factor(class))
summary(val)
```

```{r}
ggplot(Fraud) +
  geom_histogram(aes(x = purchase_value))
```
###Purchase value and frauds?
```{r}
ggplot(val) +
  geom_bar(stat = "identity", aes(x = purchase_value, y = n, fill = class), position = "dodge")
```
```{r}
ggplot(val) +
  geom_bar(stat = "identity", aes(x = purchase_value, y = n, fill = class), position = "fill")
```

```{r}
fraudss <- filter(val, class == 1)
arrange(fraudss, desc(n))
```
When the purchase value is 32 most frauds occur
