---
title: "HW1126"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

##Types of atomic vectors

###Q1

```{r}
x <- c(0, 1, NA, NaN, Inf, -Inf)
is.finite(x)
!is.infinite(x)
```
`is.finite()` returns False for NAs while `!is.infinite()` returns TRUE.

###Q2

```{r}
dplyr::near
dplyr::near(sqrt(2)^2, 2)
```
It allows the two values to be within a certain tolerance.

###Q3

```{r}
.Machine$integer.max
```

```{r}
.Machine$double.max
.Machine$double.xmax
```

###Q4

```{r}
round_down <- function(x){
  floor(x)
}

round_up <- function(x){
  ceiling(x)
}

short <- function(x){
  trunc(x)
}

far <- function(x){
  sign(x)*ceiling(abs(x))
}
```

###Q5

`parse_logical`, `parse_integer` and `parse_number`.

##Using Atomic vectors

###Q1

```{r}
x <- c(-Inf, -1, 0, 1, Inf, NA, NaN)
mean(is.na(x))
sum(!is.finite(x))
```
The first finds the number of NAs in the vector, while the second finds the number of NAs and Infs.

###Q2

`is.vector()` checks if the object has any attributes.
`is.atomic()` doesn't care if the object has an attributes.

###Q3

```{r}
setNames(1:4, c("a", "b", "c", "d"))
purrr::set_names(1:4, c("a", "b", "c", "d"))
purrr::set_names(1:4, "a", "b", "c", "d")
```

###Q4

```{r}
last_value <- function(x) {
  if (length(x)) {
    x[[length(x)]]
  } else {
    x
  }
}
last_value(1:10)
```

```{r}
even_pos <- function(x) {
  if (length(x)) {
    x[seq_along(x) %% 2 == 0]
  } else {
    x
  }
}
even_pos(1:10)
```

```{r}
not_last <- function(x) {
  if (length(x)) {
    x[-length(x)]
  } else {
    # n == 0
    x
  }
}
not_last(1:10)
```

```{r}
even_numbers <- function(x) {
  x[x %% 2 == 0]
}
even_numbers(1:11)
```

###Q5

```{r}
x <- c(-1, 0, 1, Inf, -Inf, NaN, NA)
x[-which(x > 0)]
x[x <= 0]
```
logical operation like `<=` treat NaN as NA.

###Q6

```{r}
x <- c(1:3)
x[4]
x[1:4]
x[4:5]
```

##Lists

```{r}
a <- list(a = 1:3, b = "a string", c = pi, d = list(-1, -5))
str(a[1:2])
str(a[4])
str(a[[4]])
```

```{r}
a[[4]][[1]]
```

###Q2

```{r}
x <- tibble(a = 1:2, b = 3:4)
x
x[1]
x[["b"]]
```
Tibble columns need to have consistent length, while lists can have different length.

##Augmented lists

###Q1

```{r}
x <- hms::hms(3600)
x
typeof(x)
attributes(x)
```
Print time. Double. Units and class.

###Q2

```{r}
tibble(x = 2, y = 1:5)
```
It gives a warning and won't recycle unless a value has only one elements.

###Q3

```{r}
tibble(x = 1:3, y = list("a", 1, list(1:3)))
```
It works.
