---
title: "Reading0928"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

#Exploratory Data Analysis
EDA: Question --> answers --> new question
visualization, transformation, and modeling
variable, value, observation/case, tabular data
##Visualization
Histogram
```{r}
ggplot(data = diamonds) +
      geom_histogram(mapping = aes(x = carat), binwidth = 0.5)
diamonds %>%
  count(cut_width(carat, 0.5))
```
Multiply histgram: 
```{r}
smaller <- diamonds %>%
  filter(carat < 3)
ggplot(data = smaller, mapping = aes(x = carat, color = cut)) +
      geom_freqpoly(binwidth = 0.1)
```
Use coord_cartesian to zoom in and find outlier
```{r}
 ggplot(diamonds) +
      geom_histogram(mapping = aes(x = y), binwidth = 0.5) +
      coord_cartesian(ylim = c(0, 50))
```
##Missing values
ifelse(logical statement, TRUE, FALSE)
```{r}
diamonds2 <- diamonds %>%
  mutate(y = ifelse(y < 3 | y > 20, NA, y))
ggplot(data = diamonds2, mapping = aes(x = x, y = y)) +
  geom_point(na.rm = TRUE)
```
mean() can only deal with vector/number list, not tibble.
##Covariation
variation within a variable
```{r}
ggplot(data = diamonds, mapping = aes(x = price, y = ..density..) )+
  geom_freqpoly(mapping = aes(color = cut), binwidth = 500)
```
easier to compare using boxplot, one axis is the categories while  the other axis is values
```{r}
ggplot(diamonds, aes(x = cut, y = price)) +
  geom_boxplot()
```

```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = reorder(class, hwy), y=hwy)) +
  coord_flip()
```
##Two Categorical Variables
```{r}
ggplot(data = diamonds) +
      geom_count(mapping = aes(x = cut, y = color))
```

```{r}
diamonds %>%
      count(color, cut) %>%
      ggplot(aes(x = color, y = cut)) +
        geom_tile(aes(fill = n))
```
factor() change vector to factor (numerical values to categories)
##Two Continuous Variables
```{r}
 ggplot(data = diamonds) +
      geom_point(
        mapping = aes(x = carat, y = price), alpha=1/100)
```
or bin the variable
```{r}
ggplot(data = smaller, mapping = aes(x = carat, y = price)) +
      geom_boxplot(mapping = aes(group = cut_width(carat, 0.1)))
```
or display same number of points in each bin
```{r}
 ggplot(data = smaller, mapping = aes(x = carat, y = price)) +
      geom_boxplot(mapping = aes(group = cut_number(carat, 20)))
```
or use hexbin
```{r}
 ggplot(data = smaller) +
      geom_bin2d(mapping = aes(x = carat, y = price))
 ggplot(data = smaller) +
      geom_hex(mapping = aes(x = carat, y = price))
```

##Models and Pattern
```{r}
mod <- lm(log(price) ~ log(carat), data = diamonds)
    diamonds2 <- diamonds %>%
      add_residuals(mod) %>%
      mutate(resid = exp(resid))
ggplot(data = diamonds2) +
  geom_point(mapping = aes(x = carat, y = resid))
ggplot(data = diamonds2) +
      geom_boxplot(mapping = aes(x = cut, y = resid))
```
##ggplot2 Calls
Omit data = & mapping =