---
title: "Reading40921"
output: html_document
---
#Data transformation w/ dplyr
five key dplyr functions:
filter, arrange, select, mutate, summarize
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("nycflights13")
library("Lahman")
```
##filter
###Comparison
>, <, >=, !=, ==
```{r}
filter(flights, month == 1, day == 1)
```
###Logic
and &, or |, not !
```{r}
delay <- filter(flights, !(arr_delay > 120 | dep_delay > 120))
delay
```
###NA
```{r}
df <- tibble(x = c(1, NA, 3))
filter(df, x > 1)
filter(df, is.na(x)|x > 1)
```
##arrange
for rows
```{r}
arrange(flights, year, month, day)
arrange(flights, desc(arr_delay))
arrange(flights, year, month, day, arr_delay)
```

```{r}
df <- tibble(x = c(5, 2, NA))
arrange(df, desc(x))
```

when arranging TRUE and FALSE, false goes first; descending shows the desired values to the start
```{r}
arrange(flights, desc(dep_time < 6), month)
```
##Select
for columns
```{r}
select(flights, year, month, day)
select(flights, -(year:day))
```
starts_with(), ends_with(), contains(), matches(), num_range()
```{r}
?select
```
rename
```{r}
rename(flights, tail_num = tailnum)
```
put several variables to the start.
```{r}
select(flights, day, month, year, everything())
```
##Mutate
add new columns
```{r}
flights_sml <- select(flights, year:day, ends_with("delay"), distance, air_time)
mutate(flights_sml, gain = arr_delay - dep_delay, hours = air_time / 60, gain_per_hour = gain / hours)
```
only keep new variables
```{r}
transmute(flights, dep_time, gain = arr_delay - dep_delay)
```
###Modular arithmetic
x == y * (x %/% y) + (x %% y)
```{r}
transmute(flights, dep_time, hour = dep_time %/% 100, min = dep_time %% 100)
```
log2(), log10()
offsets
```{r}
(x <- 1:10)
lead(x)
lag(x)
(x - lag(x))
```
ranking
```{r}
y <- c(1,2,2,NA,3,4) 
min_rank(y)
dense_rank(y)
```
##Summarize
```{r}
summarize(flights, delay = mean(dep_delay, na.rm = TRUE))
```

```{r}
summarize(group_by(flights, year, month, day), delay = mean(dep_delay, na.rm = TRUE))
```
###Pipe
```{r}
by_dest <- group_by(flights, dest)
delay <- summarize(by_dest, count = n(), dist = mean(distance, na.rm = TRUE), delay = mean(arr_delay, na.rm =TRUE))
delay <- filter(delay, count > 20, dest != "HNL")
ggplot(data = delay, mapping = aes(x = dist, y = delay)) +
      geom_point(aes(size = count), alpha = 1/3) +
geom_smooth(se = FALSE)
```
variable "delay": main function is summarize, inside "group_by, count, etc"
```{r}
delays <- flights %>%
group_by(dest) %>%
summarize(count = n(), dist = mean(distance, na.rm = TRUE), delay = mean(arr_delay, na.rm = TRUE)) %>%
filter(count > 20, dest != "HNL")
ggplot(data = delay, mapping = aes(x = dist, y = delay)) +
      geom_point(aes(size = count), alpha = 1/3) +
geom_smooth(se = FALSE)
```
write from inside to outside
###Missing values
na.rm; !is.na
```{r}
not_cancelled <- flights %>%
filter(!is.na(dep_delay), !is.na(arr_delay))
not_cancelled %>%
group_by(year, month, day) %>%
summarize(mean = mean(dep_delay))
```
###counts
```{r}
delays <- not_cancelled %>%
group_by(tailnum) %>%
summarize(delay = mean(arr_delay, na.rm = TRUE), n=n())
ggplot(data = delays, mapping = aes(x = n, y = delay)) +
      geom_point(alpha = 1/10)
```
###batting
```{r}
batting <- as_tibble(Lahman::Batting)
batters <- batting %>%
  group_by(playerID) %>%
summarize(ba = sum(H, na.rm = TRUE) / sum(AB, na.rm = TRUE), ab = sum(AB, na.rm = TRUE) )
batters %>%
filter(ab > 100) %>%
ggplot(mapping = aes(x = ab, y = ba)) +
  geom_point(alpha = 1 /10) +
  geom_smooth(se = FALSE)
```

```{r}
not_cancelled %>%
  count(dest)
not_cancelled %>%
  count(tailnum, wt = distance)     
```

```{r}
not_cancelled %>%
group_by(year, month, day) %>%
summarize(n_early = sum(dep_time < 500))
```
###multiple variables
*interesting* how add up only a certain month
```{r}
daily <- group_by(flights, year, month, day) 
per_day <-summarize(daily, flights=n())
(per_month <- summarize(per_day, flights = sum(flights)))
?summarize()
```
###ungroup
```{r}
daily %>%
ungroup() %>% 
summarize(flights = n())
```

##Grouping
```{r}
popular_dests <- flights %>%
        group_by(dest) %>%
        filter(n() > 365)
```

```{r}
popular_dests %>%
        filter(arr_delay > 0) %>%
        mutate(prop_delay = arr_delay / sum(arr_delay)) %>%
        select(year:day, dest, arr_delay, prop_delay)
```

