---
title: "HW191019"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nycflights13)
library(babynames)
library(nasaweather)
library(fueleconomy)
```

#Chapter 9. Tidy data with tidyr

##Tidy data

###Q1
Each variable should be put in a seperate volumn, and observations are arranged in rows.

###Q2
table2: 
```{r}
cases <- table2 %>%
  group_by(country, year) %>%
  filter(type == "cases") %>%
  rename(cases = count)
population <- table2 %>%
  group_by(country, year) %>%
  filter(type == "population") %>%
  rename(population = count)
table2.1 <- tibble(country = cases$ country, year = cases$year, cases = cases$cases, population = population$population) %>%
  mutate(rate = cases / population * 10000)
table2.1
```
table4a & 4b:
```{r}
table4.1 <- tibble(country = table4a$country, "1999rate" = table4a[['1999']] / table4b[['1999']] * 10000, "2000rate" = table4a[['2000']] / table4b[['2000']] * 10000)
table4.1
```
The table4a and 4b one is slightly easier, since we don't need to generate a new tibble to store the data.

###Q3
```{r}
table2 %>%
  filter(type == "cases") %>%
  ggplot(aes(year, count)) +
  geom_point(aes(color = country)) +
  geom_line(aes(group = country, color = "grey50"))
```
We need to find out the values of cases first.

##Gathering and spreading

###Q1
```{r}
stocks <- tibble(
year =c(2015,2015,2016,2016), half=c(1, 2, 1, 2), return = c(1.88, 0.59, 0.92, 0.17)
)
stocks
```
```{r}
stocks1 <- spread(stocks, key = half, value = return)
stocks1
```
```{r}
stocks1 %>%
  gather(key = "half", value = "return",  '1', '2')
```
The data type of the column is lost (half change from dbl to chr)
```{r}
stocks %>%
  spread(key = "half", value = "return") %>%
  gather('1', '2', key = "half", value = "return", convert = TRUE)
```
Convert turns the half to integers. Convert guesses the data type.

###Q2
You need to add "" around the 1999 and 2000 so that they can be interpreted as names.

###Q3
```{r}
people <- tribble(
  ~name, ~key, ~value,
  #-----------------|--------|------
  "Phillip Woods", "age", 45,
  "Phillip Woods", "height", 186,
  "Phillip Woods", "age", 50,
  "Jessica Cordero", "age", 37,
  "Jessica Cordero", "height", 156
)
```
spread(people, key, value)
There are two values corresponding to Phillip Woods' age.
```{r}
people1 <- people %>%
  group_by(name, key) %>%
  mutate(obs = row_number())
people1
spread(people1, key, value)
```

###Q4
```{r}
preg <- tribble(
~pregnant, ~male, ~female, "yes", NA, 10, "no", 20, 12
)
preg
```

```{r}
preg1 <- preg %>%
  gather(male, female, key = "sex", value ="count")
preg1
```

##Separate and unite

###Q1
```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>%
    separate(x, c("one", "two", "three"), extra = "merge")
```
Extra: default is dropping the extra piece and giving a warning
= "drop": simply drop the values
= "merge": put the extras into the last column.

```{r}
tibble(x = c("a,b,c", "d,e", "f,g,i")) %>%
    separate(x, c("one", "two", "three"), fill = "left")
```
Fill: when there is not enought pieces
default is give a warning and fill from the right with NA.
= "right": fill from the right
= "left": fill from the left

###Q2
```{r}
table5 %>%
    unite(Year, century, year, sep = "", remove = F)
```
"remove" removes the input values from the table. When you want to keep the old variables you can set it to FALSE.

###Q3
separate() split a column by identifying the separator, while extract() split a column by identifying the entry as following a general form with some groups within.
Because you can choose how to divide a column, but when uniting you can only choose the type of sepearator to put between.

##Missing Values

```{r}
stocks <- tibble(
year =c(2015,2015,2015,2015,2016,2016,2016), qtr =c( 1, 2, 3, 4, 2, 3, 4), return=c(1.88,0.59,0.35, NA,0.92,0.17,2.66)
)
```

###Q1
```{r}
stocks %>%
  spread(year, return, fill = "N")
stocks %>%
  complete(year, qtr, fill = list(return = "N"))
```
it can fill a list in the complete()

###Q2
```{r}
stocks %>%
  fill(return, .direction = "up")
```
It specify whether to fill NA with the previous or next value.

##WHO Case Study

###Q1
```{r}
who %>%
  filter(new_sp_m014 == 0) %>%
  nrow()
```
There is 0 cases. So missing value (NA) probably doesn't mean 0 case occurs for that category; it means WHO don't have the data. Thus it's reasonable to ignore it.

###2
```{r}
who
who1 <- who %>%
  gather(new_sp_m014:newrel_f65, key = "key", value = "cases",
na.rm = TRUE) %>%
  separate(key, c("new", "type", "sexage"), sep = "_") %>%
  select(-new) %>%
  separate("sexage", c("sex", "age"), sep = 1)
who1
```
It gives out a warning, because it cannot sort out new_rel using that separate method.

###Q3
```{r}
select(who1, country, iso2, iso3) %>%
  distinct() %>%
  group_by(country) %>%
  filter(n() > 1)
```
There is no distinct combination of iso2 and iso3 for each country, so iso2 and iso3 are indeed only abbr.

###Q4
```{r}
who2 <- who1 %>%
  group_by(country, year, sex) %>%
  summarise(cases = sum(cases)) %>%
  unite(countrysex, country, sex, remove = F) %>%
  filter(year > 1995) 
```

```{r}
ggplot(who2, aes(x = year, y = cases, group = countrysex, colour = sex)) +
  geom_line()
```

#Chapter 10 Relational Data with dplyr

##nycflights13

###Q1
flights and airports; flights give you the flights of plane and its departing and arriving airports, while airports gives the longitude and latitude of those airports. origin&dest in flights and faa&lat&lon in airports.

###Q2
origin in weather --> faa in airports

###Q3
origin in weather --> dest in flights, both share time.

###Q4
```{r}
holidays <- tribble(
  ~name, ~year, ~month, ~day,
  "New year", 2013, 01, 01, 
  "July 4th", 2013, 07, 04, 
  "Thanksgiving", 2013, 11, 29,
  "Chrismas", 2013, 12, 25
)
```
Date and name. Date can be used to map to existing tables.

##Keys

###Q1
```{r}
flights1 <- flights %>%
  arrange(year, month, day, sched_dep_time, flight) %>%
  mutate(id = row_number())
flights1 %>%
  distinct() %>%
  group_by(id) %>%
  filter(n() > 1)
```

###Q2
a. playerID, teamID, yearID, and stint
```{r}
Batting <- Lahman::Batting
```

```{r}
Batting %>% 
  distinct() %>%
  group_by(playerID, teamID, yearID, stint) %>%
  filter(n() > 1)
```

b. year, name, sex
```{r}
names <- babynames::babynames
```

```{r}
names %>%
  group_by(year, name, sex) %>%
  count() %>%
  filter(n > 1) %>%
  nrow()
```

c. lat, long, year, month
```{r}
atmos <- nasaweather::atmos
atmos %>%
  group_by(lat, long, year, month) %>%
  count() %>%
  filter(n > 1) %>%
  nrow()
```

d. the number of distinct combinations is smaller than the total number of rows.
```{r}
ggplot2::diamonds %>%
  distinct() %>%
  nrow()
nrow(ggplot2::diamonds)
```

###Q3
Batting -- Master: PlayerID. Batting -- Salaries: PlayerID, yearID, teamID, igID; add Salaries to Batting; 
```{r}
Master <- Lahman::Master
Salaries <- Lahman::Salaries
```
All of the Batting, Fielding, and Pitching have PlayerID, yearID, and stint.

##Mutating Joins
```{r setup, include=FALSE}
flights2 <- flights %>%
  select(year:day, hour, origin, dest, tailnum, carrier)
flights2
```

###Q1
```{r}
delay <- flights %>%
  group_by(dest) %>%
  summarise(depdelay = mean(dep_delay, na.rm = TRUE)) %>%
  inner_join(airports, by = c(dest = "faa")) %>%
  select(dest, depdelay, lon, lat) %>%
  ggplot(aes(lon, lat)) +
    geom_point(aes(color = depdelay)) +
    borders("state") +
    coord_quickmap()
delay
```

###Q2
```{r}
locations <- airports %>%
  select(faa, lat, lon)
flights %>%
  select(year:day, hour, origin, dest) %>%
  left_join(locations, by = c("origin" = "faa")) %>%
  left_join(locations, by = c("dest" = "faa"), suffix = c("_origin", "_dest"))
```

###Q3
```{r}
age <- select(planes, tailnum, productyear = year)
flights2 <- flights %>%
  inner_join(age, by = "tailnum") %>%
  mutate(age1 = year - productyear) %>%
  group_by(age1) %>%
  summarize(dep_delay_mean = mean(dep_delay, na.rm = TRUE),
    dep_delay_sd = sd(dep_delay, na.rm = TRUE),
    arr_delay_mean = mean(arr_delay, na.rm = TRUE),
    arr_delay_sd = sd(arr_delay, na.rm = TRUE),
    n_arr_delay = sum(!is.na(arr_delay)),
    n_dep_delay = sum(!is.na(dep_delay)))
flights2
```

```{r}
ggplot(flights2) +
  geom_point(aes(age1, dep_delay_mean, color = "dep")) +
   geom_point(aes(age1, arr_delay_mean, color = "arr")) 
```

###Q4
```{r}
flights %>%
  inner_join(weather) %>%
  group_by(precip) %>%
  summarise(delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = precip, y = delay)) +
  geom_line() + geom_point()
```

###Q5
there were derechos.
```{r}
delay1 <- flights %>%
  filter(year == 2013, month == 6, day == 13) %>%
  group_by(dest) %>%
  summarise(depdelay = mean(dep_delay, na.rm = TRUE)) %>%
  inner_join(airports, by = c(dest = "faa")) %>%
  select(dest, depdelay, lon, lat) %>%
  ggplot(aes(lon, lat)) +
    geom_point(aes(size = depdelay, color = depdelay)) +
    borders("state") +
    coord_quickmap() +
   scale_color_viridis_c()
delay1
```

##Filter-join

###Q1
flights with missing tailnums also miss the dep&arr and airtime. They are probably being cancelled.
```{r}
filter(flights, is.na(tailnum))
```

###Q2
```{r}
flights %>%
  inner_join(weather) %>%
  group_by(precip) %>%
  summarise(delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = precip, y = delay)) +
  geom_line() + geom_point()
```