---
title: "HW202008_Ch4"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(class)
library(ISLR)
library(dplyr)
```

## Chapter 4 Applied

###Q10

```{r}
attach(Weekly)
glimpse(Weekly)
```

####a)

```{r}
cor(Weekly[, -9])
pairs(Weekly)
```
Only the correlation between year and volume is quite significant. Volume increases over time.
```{r}
plot(Year, Volume)
```

```{r}
plot(Volume)
```

####b)

```{r}
fit.glm <- glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, data = Weekly, family = binomial)
summary(fit.glm)
```

####c)

```{r}
probs <- predict(fit.glm, type = "response")
pred.glm <- rep("Down", length(probs))
pred.glm[probs > 0.5] <- "Up"
table(pred.glm, Direction)
```

```{r}
right = (54+557)/(54+48+430+557)
right
```

####d) logistic regression

```{r}
train <- (Year < 2009)
test <- Weekly[!train, ]
test_direction <- Direction[!train]
fit.glm2 <- glm(Direction ~ Lag2, data = Weekly, family = binomial, subset = train)
summary(fit.glm2)
```

```{r}
probs2 <- predict(fit.glm2, test, type = "response")
pred.glm2 <- rep("Down", length(probs2))
pred.glm2[probs2 > 0.5] <- "Up"
table(pred.glm2, test_direction)
```

```{r}
1-(9+56)/(9+5+34+56)
```
test error is 0.375

####e) LDA

```{r}
fit.lda <- lda(Direction ~ Lag2, data = Weekly, subset = train)
fit.lda
```

```{r}
pred.lda <- predict(fit.lda, test)
table(pred.lda$class, test_direction)
```
the same with logistic regression model.

####f) QDA

```{r}
fit.qda <- qda(Direction ~ Lag2, data = Weekly, subset = train)
fit.qda
```

```{r}
pred.qda <- predict(fit.qda, test)
table(pred.qda$class, test_direction)
```
Always predict Up.
```{r}
1-61/(43+61)
```

####g) KNN, K=1

```{r}
train.X <- as.matrix(Lag2[train])
test.X <- as.matrix(Lag2[!train])
train_direction <- Direction[train]
set.seed(1)
pred.knn <- knn(train.X, test.X, train_direction, k = 1)
table(pred.knn, test_direction)
```

```{r}
1-(21+31)/(21+30+22+31)
```
error rate 0.5

####h) logistic = LDA > QDA > KNN

###Q11

```{r}
attach(Auto)
glimpse(Auto)
```

####a)

```{r}
mpg01 <- rep(0, length(mpg))
mpg01[mpg > median(mpg)] <- 1
Auto1 <- data.frame(Auto, mpg01)
```

```{r}
cor(Auto1[, -9])
```

```{r}
pairs(Auto1)
```

####b) Cylinders, weight, displacement, horsepower.

####c)

```{r}
train <- (year %% 2 == 0)
Auto.train <- Auto[train, ]
Auto.test <- Auto[!train, ]
mpg01.test <- mpg01[!train]
```

####d) lda

```{r}
fit.lda <- lda(mpg01 ~ cylinders + weight + displacement + horsepower, data = Auto, subset = train)
fit.lda
```

```{r}
pred.lda <- predict(fit.lda, Auto.test)
table(pred.lda$class, mpg01.test)
```

```{r}
mean(pred.lda$class != mpg01.test)
```

####e) qda

```{r}
fit.qda <- qda(mpg01 ~ cylinders + weight + displacement + horsepower, data = Auto, subset = train)
fit.qda
```

```{r}
pred.qda <- predict(fit.qda, Auto.test)
table(pred.qda$class, mpg01.test)
mean(pred.qda$class != mpg01.test)
```

####f) logistic

```{r}
fit.glm <- glm(mpg01 ~ cylinders + weight + displacement + horsepower, data = Auto, family = binomial, subset = train)
summary(fit.glm)
```

```{r}
probs <- predict(fit.glm, Auto.test, type = "response")
pred.glm <- rep(0, length(probs))
pred.glm[probs > 0.5] <- 1
table(pred.glm, mpg01.test)
mean(pred.glm != mpg01.test)
```

####g) KNN

```{r}
train.X <- cbind(cylinders, weight, displacement, horsepower)[train, ]
test.X <- cbind(cylinders, weight, displacement, horsepower)[!train, ]
train.mpg01 <- mpg01[train]
```

K=1
```{r}
set.seed(1)
pred.knn <- knn(train.X, test.X, train.mpg01, k = 1)
table(pred.knn, mpg01.test)
mean(pred.knn != mpg01.test)
```

K=5
```{r}
set.seed(1)
pred.knn5 <- knn(train.X, test.X, train.mpg01, k = 5)
table(pred.knn5, mpg01.test)
mean(pred.knn5 != mpg01.test)
```

K=10
```{r}
set.seed(1)
pred.knn10 <- knn(train.X, test.X, train.mpg01, k = 10)
table(pred.knn10, mpg01.test)
mean(pred.knn10 != mpg01.test)
```

###Q12

####a)

```{r}
power <- function(){
  2^3
}
power()
```

####b)

```{r}
power2 <- function(x, a){
  x^a
}
power2(2, 3)
```

####c)

```{r}
power2(10, 3)
power2(8, 17)
power2(131, 3)
```

####d)

```{r}
power3 <- function(x , a) {
    result <- x^a
    return(result)
}
power3(2, 3)
```

####e)

```{r}
x <- 1:10
plot(x, power3(x, 3))
plot(x, power3(x, 3), log = "y")
```

####f)

```{r}
plotpower <- function(x, a){
  plot(x, power3(x, a))
}
plotpower(1:10, 3)
```

###Q13

####a)

```{r}
attach(Boston)
crim01 <- rep(0, length(crim))
crim01[crim > median(crim)] <- 1
boston <- data.frame(Boston, crim01)
```

train and test
```{r}
train <- 1:(length(crim)*2/3)
test <- (length(crim)*2/3 + 1):length(crim)
boston.train <- boston[train, ]
boston.test <- boston[test, ]
crim01.test <- crim01[test]
```

####logistic

```{r}
fit.glm <- glm(crim01 ~ . - crim01 - crim, data = Boston, subset = train)
summary(fit.glm)
```

```{r}
fit.glm1 <- glm(crim01 ~ nox + age + rad + ptratio, data = Boston, subset = train)
summary(fit.glm1)
```

```{r}
probs <- predict(fit.glm1, boston.test, "response")
pred.glm1 <- rep(0, length(probs))
pred.glm1[probs > 0.5] <- 1
table(pred.glm1, crim01.test)
```

####lda

```{r}
fit.lda1 <- lda(crim01 ~ nox + age + rad + ptratio, data = boston.train)
pred.lda1 <- predict(fit.lda1, boston.test)
table(pred.lda1$class, crim01.test)
```

####qda

```{r}
fit.qda1 <- qda(crim01 ~ nox + age + rad + ptratio, data = boston.train)
pred.qda1 <- predict(fit.qda1, boston.test)
table(pred.qda1$class, crim01.test)
```

####KNN

```{r}
train.c <- cbind(nox, age, rad, ptratio)[train, ]
test.c <- cbind(nox, age, rad, ptratio)[test, ]
train.crim01 <- crim01[train]
```

k=1
```{r}
set.seed(121)
pred.knn1 <- knn(train.c, test.c, train.crim01, k = 1)
table(pred.knn1, crim01.test)
```
k=9
```{r}
pred.knn9 <- knn(train.c, test.c, train.crim01, k = 9)
table(pred.knn9, crim01.test)
```

k=15
```{r}
pred.knn15 <- knn(train.c, test.c, train.crim01, k = 15)
table(pred.knn15, crim01.test)
```

####compare

```{r}
mean(pred.glm1 != crim01.test)
mean(pred.lda1$class != crim01.test)
mean(pred.qda1$class != crim01.test)
mean(pred.knn9 != crim01.test)
```

