---
title: "apron_ty"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(recommenderlab)
library(data.table)
library(lubridate)
library(reshape2)
library(dplyr)
```

## Import

Here I use dataset from https://www.kaggle.com/azathoth42/myanimelist 
It contains: basic information of 6668 anime (overall rating, number of episodes, airing year, genres, etc), information of 108711 users, and the rating they gave for each anime they???ve watched or watching.

```{r}
anime <- read.csv("clean/anime_cleaned.csv")
lists <- read.csv("clean/animelists_cleaned.csv")
```

I only select the variables useful for making the recommendation system, excluding info. related to the content of animes and variables lacked documentation or uniform formats. 
Some animes that do not have ratings or minutes (i.e. not actually an anime) are excluded as well.

```{r}
Anime <- anime %>%
  select("anime_id":"title", "type":"status", "rating":"popularity", "favorites", "studio", "genre", "duration_min":"aired_from_year") %>%
  filter(duration_min != 0)  %>%
  filter("scored_by" != 0)
```

```{r}
Lists <- lists %>%
  select("username", "anime_id", "my_score") %>%
  filter("my_score" != 0)
```

## Exploration

Overall distribution of ratings.

```{r}
ggplot(Anime) +
  geom_histogram(aes(score))
```

What are the animes with highest score? When someone is completely new to anime they can perhaps try these. 

```{r}
head(arrange(Anime, score))
```
Seasonal animes (less than 26 episodes) and highest rating.

```{r}
head(Anime %>%
	filter(episodes < 26&episodes >0) %>%
	arrange(score))
```

This part does not have so much connection with building the recommendation system but I???m interested???
People always say that light novels??? adoption is the worst. But here it shows not really. 

```{r}
ggplot(Anime) +
  geom_boxplot(aes(type, score))
ggplot(Anime) +
  geom_boxplot(aes(rating, score))
ggplot(Anime) +
  geom_boxplot(aes(source, score))
```

## Some Preprocessing

Split the genre column in Anime into a data frame (where 1 means an anime belongs to this genre and 0 means it does not)

```{r}
genres <- as.data.frame(Anime$genre, stringsAsFactors=FALSE)
genres2 <- as.data.frame(tstrsplit(genres[,1], '[,]', 
                                   type.convert=TRUE), 
                         stringsAsFactors=FALSE)
colnames(genres2) <- c(1:13)
```

```{r}
genre_list <- c("Action", "Adventure", "Cars", "Comedy", "Dementia","Demons", "Drama", "Ecchi", "Fantasy","Game", "Harem", "Hentai", "Historical","Horror", "Josei", "Kids", "Magic", "Martial Arts", "Mecha", "Military", "Music", "Mystery", "Parody", "Police", "Psychological", "Romance", "Samurai", "School", "Sci-Fi", "Seinen", "Shoujo", "Shoujo Ai", "Slice of Life", "Space", "Sports", "Super Power", "Supernatural", "Thriller", "Vampire", "Yaoi", "Yuri")
```

```{r}
genre_matrix <- matrix(0,6622,41)
genre_matrix[1,] <- genre_list 
colnames(genre_matrix) <- genre_list 
for (i in 1:nrow(genres2)) {
  for (c in 1:ncol(genres2)) {
    genmat_col = which(genre_matrix[1,] == genres2[i,c])
    genre_matrix[i+1, genmat_col] <- 1
  }
}
```

```{r}
genre_matrix2 <- as.data.frame(genre_matrix[-1,], stringsAsFactors=FALSE)
for (c in 1:ncol(genre_matrix2)) {
  genre_matrix2[,c] <- as.integer(genre_matrix2[,c])
} 
```
Rejoin this with the anime data frame.

```{r}
anime_index <- cbind(Anime, genre_matrix2)
```

## User based collaborative filtering

Basic idea of UBCF:
1. Creating a matrix that has username as rows and anime_id as columns, and ratings as entries.
2. Some transformation to reduce the magnitude of the matrix/normalization
3. For each user, find users who have ???similar taste??? to him/her, then use their rating to recommend animes to him/her.
I will use a package called recommenderlab to do this.

First of all, transform the data frame to a matrix for recommender lab to work.

```{r}
ratingmat <- dcast(Lists, username~anime_id, value.var = "my_score", na.rm=FALSE)
ratingmat <- as.matrix(ratingmat[,-1])
ratingmat <- as(ratingmat, "realRatingMatrix")
```

### Some visualization

Similarity between users:

```{r}
similarity_users <- similarity(ratingmat[1:4, ], 
                               method = "cosine", 
                               which = "users")
similarity_users <- as.matrix(similarity_users)
image(as.matrix(similarity_users), main = "User similarity")
```

*```{r}
*image(ratingmat, main = "Heatmap of the rating matrix") # too many
*```

### Pre-process

Here I select users who have watched enough animes to make recommendation (and animes with enough ratings, intended to use for item-based collaborative filtering)

```{r}
ratingmat2 <- ratingmat[rowCounts(ratingmat) > 15, colCounts(ratingmat) > 100]
```

#### Normalization

Some users might incline to leave higher or lower ratings for all the anime he/she watched. So here I normalize everyone???s rating so each one???s ratings have the mean 0 and sd of 1.

```{r}
ratingmat3 <- normalize(ratingmat2)
sum(rowMeans(ratingmat3) > 0.1)
```
Only one user???s mean is bigger than 0.1, so I will say the normalization works.

#### Binarization

Because the MAL has ratings from 1 to 10, and the matrix is quite large (6000*9000), so binarization can reduce its size for making models.

```{r}
ratingmat4 <- binarize(ratingmat3, minRating = 0)
```
This set is just to make sure again each person have enough positive values for making the model.

```{r}
ratingmat5 <- ratingmat4[rowSums(ratingmat4) > 6,]
```

#### Splitting

I put 80% of each person???s data into the train set and others into the test set. If they do not have enough entries, at least five values are put into the test set.

```{r}
eval_sets = evaluationScheme(data = ratingmat5, method = "split", train = 0.8, given = -5)
```

```{r}
eval_sets1 = evaluationScheme(data = ratingmat5[1:10000,], method = "split", train = 0.8, given = -5)
```

### Building Rec 

```{r}
user_recommender = Recommender(data = getData(eval_sets, "train"),
                               method = "UBCF", parameter = NULL)
```

```{r}
getModel(user_recommender)
```
Use it to make prediction:

```{r}
user_prediction = predict(object = user_recommender,
                          newdata = getData(eval_sets, "known"),
                          n = 1,
                          type = "ratings")
```

Calculate its accuracy:

```{r}
user_pred <- getTopNLists(x = user_prediction, n=5)
```

```{r}
user_accuracy = calcPredictionAccuracy(x = user_pred, given = 5,
                                       data = getData(eval_sets, "unknown"), byUser=T)
user_accuracy
```

## Item Based Collaborative Filtering 

IBCF's idea is basically the same as UBCF, but takes much much longer time...
```{r}
# item_recommender = Recommender(data = getData(eval_sets1, "train"),
#                                method = "IBCF", parameter = NULL)
```

```{r}
# getModel(item_recommender)
```
Use it to make prediction:

```{r}
# item_prediction = predict(object = item_recommender,
#                          newdata = getData(eval_sets1, "known"),
#                          n = 1,
#                          type = "ratings")
```

Calculate its accuracy:

```{r}
# item_pred <- getTopNLists(x = item_prediction, n = 200)
```

```{r}
# item_accuracy = calcPredictionAccuracy(x = user_pred, given = 200,
#                                        data = getData(eval_sets1, "unknown"), byUser=T)
# item_accuracy
```

## Comparison with models with other parameters

```{r}
models_to_evaluate = list(UBCF_cos = list(name = "UBCF", param = list(method = "cosine")),
                          UBCF_cor = list(name = "UBCF", param = list(method = "pearson")),
                          random = list(name = "RANDOM", param=NULL))
n_recommendations = c(1, 3, 5, 10)
results = evaluate(x = eval_sets1, method = models_to_evaluate, n = n_recommendations)
```

```{r}
plot(results, y = "ROC", annotate = 1, legend="topleft")
title("ROC Curve")
```

```{r}
plot(results, y = "prec/rec", annotate=1)
title("Precision-Recall")
```

## Item rec based on Anime/user info

The idea is to do clustering on animes based on their genre, studio, airing year. Then recommend animes in the same cluster to the user.

There is a data frame contains the age, gender, etc., of the user. This info may be useful for recommendation.
