---
title: "aproj"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(recommenderlab)
library(data.table)
library(lubridate)
library(reshape2)
library(dplyr)
```

## Import

```{r}
anime <- read.csv("clean/anime_cleaned.csv")
user <- read.csv("clean/users_cleaned.csv")
lists <- read.csv("clean/animelists_cleaned.csv")
```

I only select the variables useful for making the recommendation system, excluding info. related to the content of animes and variables lacked documentation or uniform formats. 

```{r}
Anime <- anime %>%
  select("anime_id":"title", "type":"status", "rating":"popularity", "favorites", "producer", "studio", "genre", "duration_min":"aired_from_year") %>%
  filter(duration_min != 0)  %>%
  filter("scored_by" != 0)
```

```{r}
Users <- user %>%
  select("username", "user_id", "user_days_spent_watching":"gender", "birth_date", "stats_mean_score", "stats_episodes") %>%
  mutate("birth_date" = year(as_date(ymd_hms(as.character.Date(birth_date)))))
```

```{r}
Lists <- lists %>%
  select("username", "anime_id", "my_score") %>%
  filter("my_score" != 0)
```


## Exploration

```{r}
head(arrange(Anime, score))
```

```{r}
ggplot(Anime) +
  geom_histogram(aes(score))
```

```{r}
ggplot(Anime) +
  geom_boxplot(aes(type, score))
ggplot(Anime) +
  geom_boxplot(aes(rating, score))
ggplot(Anime) +
  geom_boxplot(aes(source, score))
```

## Some Preprocessing

Split the genre column in Anime into a dataframe to later join with
```{r}
genres <- as.data.frame(Anime$genre, stringsAsFactors=FALSE)
genres2 <- as.data.frame(tstrsplit(genres[,1], '[,]', 
                                   type.convert=TRUE), 
                         stringsAsFactors=FALSE)
colnames(genres2) <- c(1:13)
```

```{r}
genre_list <- c("Action", "Adventure", "Cars", "Comedy", "Dementia","Demons", "Drama", "Ecchi", "Fantasy","Game", "Harem", "Hentai", "Historical","Horror", "Josei", "Kids", "Magic", "Martial Arts", "Mecha", "Military", "Music", "Mystery", "Parody", "Police", "Psychological", "Romance", "Samurai", "School", "Sci-Fi", "Seinen", "Shoujo", "Shoujo Ai", "Slice of Life", "Space", "Sports", "Super Power", "Supernatural", "Thriller", "Vampire", "Yaoi", "Yuri")
```

```{r}
genre_matrix <- matrix(0,6622,41)
genre_matrix[1,] <- genre_list 
colnames(genre_matrix) <- genre_list 
for (i in 1:nrow(genres2)) {
  for (c in 1:ncol(genres2)) {
    genmat_col = which(genre_matrix[1,] == genres2[i,c])
    genre_matrix[i+1, genmat_col] <- 1
  }
}
```

```{r}
genre_matrix2 <- as.data.frame(genre_matrix[-1,], stringsAsFactors=FALSE)
for (c in 1:ncol(genre_matrix2)) {
  genre_matrix2[,c] <- as.integer(genre_matrix2[,c])
} 
```

Do the same for producer

```{r}
producers <- as.data.frame(Anime$producer, stringsAsFactors=FALSE)
producers2 <- as.data.frame(tstrsplit(producers[,1], '[,]', 
                                   type.convert=TRUE), 
                         stringsAsFactors=FALSE)
colnames(producers2) <- c(1:13)
producer_df <- distinct_at(producers2,"1")
producer_list <- as.character(producer_df[,1])
```

```{r}
producer_matrix <- matrix(0,6622,455)
producer_matrix[1,] <- producer_list 
colnames(producer_matrix) <- producer_list 
for (i in 1:nrow(producers2)) {
  for (c in 1:ncol(producers2)) {
    promat_col = which(producer_matrix[1,] == producers2[i,c])
    producer_matrix[i+1, promat_col] <- 1
  }
}

producer_matrix2 <- as.data.frame(producer_matrix[-1,], stringsAsFactors=FALSE)
for (c in 1:ncol(producer_matrix2)) {
  producer_matrix2[,c] <- as.integer(producer_matrix2[,c])
} 
colnames(producer_matrix2) <- producer_list 
```

```{r}
anime_index <- cbind(Anime, genre_matrix2) %>%
  cbind(producer_matrix2)
anime_index <- anime_index[,!(names(anime_index)) %in% c("producer", "genre")]
```

## User based collaborative filtering

### Hot matrix

```{r}
ratingmat <- dcast(Lists, username~anime_id, value.var = "my_score", na.rm=FALSE)
ratingmat <- as.matrix(ratingmat[,-1])
ratingmat <- as(ratingmat, "realRatingMatrix")
```

Similarity between users:

```{r}
similarity_users <- similarity(ratingmat[1:4, ], 
                               method = "cosine", 
                               which = "users")
similarity_users <- as.matrix(similarity_users)
image(as.matrix(similarity_users), main = "User similarity")
```

*```{r}
*image(ratingmat, main = "Heatmap of the rating matrix") # hard to read-too many *dimensions
*```

```{r}
image(ratingmat[1:10, 1:15], main = "Heatmap of the first rows and columns")
image(ratingmat[rowCounts(ratingmat) > quantile(rowCounts(ratingmat), 0.99),
                 colCounts(ratingmat) > quantile(colCounts(ratingmat), 0.99)], 
      main = "Heatmap of the top users and animes")
```

### Pre-process

```{r}
ratingmat2 <- ratingmat[rowCounts(ratingmat) > 15, colCounts(ratingmat) > 100]
```

Normalized the ratings of each user
```{r}
ratingmat3 <- normalize(ratingmat2)
sum(rowMeans(ratingmat3) > 0.1)
```

Binarize
```{r}
ratingmat4 <- binarize(ratingmat3, minRating = 0)
```

```{r}
ratingmat5 <- ratingmat4[rowSums(ratingmat4) > 6,]
```

Splitting into train and test sets
```{r}
eval_sets = evaluationScheme(data = ratingmat5, method = "split",
                             train = 0.8, given = -5)
```

### Building Rec

```{r}
user_recommender = Recommender(data = getData(eval_sets, "train"),
                               method = "UBCF", parameter = NULL)
```

```{r}
getModel(user_recommender)
```

```{r}
user_prediction = predict(object = user_recommender,
                          newdata = getData(eval_sets, "known"),
                          n = 5,
                          type = "ratings")
```

```{r}
user_accuracy = calcPredictionAccuracy(x = user_prediction,
                                       data = getData(eval_sets, "unknown"),
                                       byUser = TRUE)
head(user_accuracy)
```

## Item based collaborative filtering

Similarity between animes:

```{r}
similarity_items <- as.matrix(similarity(ratingmat[, 1:4], method =
                                 "cosine", which = "items"))
image(as.matrix(similarity_items), main = "Movies similarity")
```

### Heat matrix

```{r}
# image(ratingmat, main = "Heatmap of the rating matrix") # too many
image(ratingmat[1:20, 1:25], main = "Heatmap of the first 20 rows and 25 columns")
image(ratingmat5[1:20, 1:25], main = "Heatmap of the first 20 rows and 25 columns")
```

### Building Rec

```{r}
# item_recommender = Recommender(data = getData(eval_sets, "train"),
#                                method = "IBCF", parameter = NULL)
```

```{r}
# getModel(item_recommender)
```

```{r}
# item_prediction = predict(object = item_recommender,
#                          newdata = getData(eval_sets, "known"),
#                          n = 5,
#                          type = "ratings")
```

```{r}
#item_accuracy = calcPredictionAccuracy(x = item_prediction,
#                                       data = getData(eval_sets, "unknown"),
#                                       byUser = TRUE)
#head(item_accuracy)
```

## Comparison

```{r}
models_to_evaluate = list(UBCF_cos = list(name = "UBCF", param = list(method = "cosine")),
                          UBCF_cor = list(name = "UBCF", param = list(method = "pearson")),
                          random = list(name = "RANDOM", param=NULL))

n_recommendations = c(1, 3, 5, 10, 15)
results = evaluate(x = eval_sets, method = models_to_evaluate, n = n_recommendations)
```

```{r}
plot(results, y = "ROC", annotate = 1, legend="topleft")
title("ROC Curve")
```

```{r}
plot(results, y = "prec/rec", annotate=1)
title("Precision-Recall")
```


## Item rec based on Anime info

```{r}
set.seed(16)
in_train <- sample(dim(anime_index)[1], dim(anime_index)[1] * 0.8)
train_ani <- anime_index[in_train, ]
test_ani <- anime_index[-in_train, ]
```

### PCA

```{r}
pca_ani <- prcomp(train_ani, scale = TRUE)
```

```{r}
pve=100*pca_ani$sdev^2/sum(pca_ani$sdev^2)
par(mfrow=c(1,2))
plot(pve, type="o", ylab="PVE", xlab="Principal Component",
col =" blue ")
plot(cumsum(pve), type="o", ylab="Cumulative PVE", xlab="
Principal Component ", col =" brown3 ")
```

```{r}
comp <- data.frame(pca_ani$x[,1:4])
plot(comp, pch=16, col=rgb(0,0,0,0.5))
```

### kmeans

number of clusters
```{r}
wss <- (nrow(mydata)-1)*sum(apply(mydata,2,var))
```

```{r}
for (i in 2:15){wss[i] <- sum(kmeans(mydata,
   centers=i)$withinss)
}
```

```{r}
plot(1:15, wss, type="b", xlab="Number of Clusters", ylab="Within groups sum of squares")
```

```{r}
k <- kmeans(comp, 4, nstart=25, iter.max=1000)
```

```{r}
anime_f <- cbind(Anime, k$clusters)
```

